Untrusted B2B Collaboration using the Blockchain

### 2018-07-30 paper/paper.tex
Minor stuff

\begin{table}
	\centering
	\caption{Gas used by contracts in the example choreography.} \label{gasusage}
	\begin{tabular}{|l | c | c | c|}
		\hline                          & \textbf{Factory} & \textbf{Instance} & \textbf{Sum}       \\
		\hline \textbf{Bulk Buyer}      & 4,590,569        & 59,396            & 4,649,965          \\
		\hline \textbf{Manufacturer}    & 129,588          & 124,316           & 253,904            \\
		\hline \textbf{Middleman}       & 129,586          & 111,189           & 240,775            \\
		\hline \textbf{Supplier}        & 86,398           & 61,745            & 148,143            \\
		\hline \textbf{Special Carrier} & 86,376           & 81,945            & 168,321            \\
		\hline \textbf{Sum}             & 5,022,517        & 438,591           & \textbf{5,461,108} \\ \hline
	\end{tabular}
\end{table}
Because of highly fluctuating exchange rates of USD to ether and ether to gas, the total gas cost varies as well. At the time of writing the total cas cost amounted to \$2.50 according to \url{ethgasstation.info}. 
Most of the transactions have proven to come with reasonable gas costs.
However, the instantiation cost that is currently paid by the initiator appears to be problematic.
As the first instantiation transitively triggers all the other participant's instantiations, this can become quite costly, and might even surpass the \emph{block gas limit}, the maximum amount of gas that can be spent per new block, depending on the number of participants involved.
%Even if that is not the case, a high gas cost is still a problem, since in Ethereum, by design, transactions with high gas costs are less likely to be included in a block by miners, possibly leading to long waiting times. % TODO why again?

>>>>

\begin{table}
	\centering
	\caption{Gas used by contracts in the example choreography.} \label{gasusage}
	\begin{tabular}{|l | c | c | c|}
		\hline                          & \textbf{Factory} & \textbf{Instance} & \textbf{Sum}       \\
		\hline \textbf{Bulk Buyer}      & 4,590,569        & 59,396            & 4,649,965          \\
		\hline \textbf{Manufacturer}    & 129,588          & 124,316           & 253,904            \\
		\hline \textbf{Middleman}       & 129,586          & 111,189           & 240,775            \\
		\hline \textbf{Supplier}        & 86,398           & 61,745            & 148,143            \\
		\hline \textbf{Special Carrier} & 86,376           & 81,945            & 168,321            \\
		\hline \textbf{Sum}             & 5,022,517        & 438,591           & \textbf{5,461,108} \\ \hline
	\end{tabular}
\end{table}

Because of fluctuating exchange rates of USD to Ether and Ether to gas, the total gas cost varies.
At the time of writing the total cas cost amounted to \$2.50 according to \url{https://ethgasstation.info}, based on a gas exchange rate of 1 gas = 1 Gwei.

Most of the transactions have proven to come with reasonable gas costs.
However, the instantiation cost that is currently paid by the initiator appears to be problematic.
As the first instantiation transitively triggers all the other participant's instantiations, this can become quite costly, and might even surpass the \emph{block gas limit}, the maximum amount of gas that can be spent per new block, depending on the number of participants involved.
%Even if that is not the case, a high gas cost is still a problem, since in Ethereum, by design, transactions with high gas costs are less likely to be included in a block by miners, possibly leading to long waiting times. % TODO why again?
